\beginsong{I Wanna' Go Home}[by={Akane Sasu Sora}]

\newchords{verse}
\newchords{chorus}
\newchords{bridge}

\beginverse\memorize[verse]
\[C]Leaving in the \[Em]morning, with\[F]out a word to \[C]say
\[F]from my house in\[Em]to the \[Am]world, \[F]in the light of \[G]day
\[C]I might seem cou\[Em]rageous, but \[F]once the sun goes \[C]down
\[F]you'll find that \[Em]I'm the biggest\[Am] \[F]cry\[G]baby \[C]around...
\endverse

\beginverse\replay[verse]
^Skies above the ^city, ^painted a lovely ^red
^Crows and pigeons ^call as ^they ^soar over my ^head
^I can see my ^shadow ^growing against the ^trees
^Right now more than ^any^thing, ^I ^just wanna ^leave.
\endverse

\beginverse\memorize[bridge]
\[F]Are you grilling fish? \[C]Somehow I can tell...
\[F]Is that for \[D]dinner? \[G]What a lovely smell...
\endverse

\beginchorus\memorize[chorus]
\[C]Hear my tummy \[Emi]rumble... It's \[F]crying out for \[C]food
\[F]I should just \[Em]apolo\[Ami]gize. \[F]I know I was \[G]rude...
\[C]Why am I so \[Emi]stubborn? \[F]Why do I cry and \[E]moan?
Aah, \[F]there's one thing I \[Emi]want right \[Ami]now: \[F]I \[G]wanna go \[C]home!
\endchorus

\beginverse\replay[verse]
^On the other ^side of ^the road, I see a ^child,
^parents nowhere ^to be ^found, ^sobbing, running ^wild
^I just keep on ^walking. ^Familiar, she ^seemed...
^Crying, far a^way from ^home... oh ^wait ^thats ^me
\endverse

\beginverse\replay[bridge]
^And as my shadow ^fades into the dark
^I hear a ^voice calling ^deep within my heart
\endverse

\beginverse\replay[chorus]
^So I start to ^run and ^I wipe my tears ^dry
^chasing after ^Mr. ^Moon, ^waving me good^bye
^If I say I'm ^sorry ^before they go to ^bed
Aah, when I get home, there might still
be some dinner left!
\endverse

\beginverse\replay[bridge]
^Fish being grilled, ^scents linger in the air
^A homecooked ^meal! Ahh, ^I wanna be there!
\endverse

\beginchorus
\[C]Hear my tummy \[Emi]rumble... It's \[F]crying out for \[C]food
\[F]I should just \[Em]apolo\[Ami]gize. \[F]I know I was \[G]rude...
\[C]Why am I so \[Emi]stubborn? \[F]Why do I cry and \[E]moan?
Aah, \[F]there's one thing I \[Emi]want right \[Ami]now: \[F]I \[G]wanna go \[C]home!
\endchorus

\endsong
