\begin{song}{I'm Just Ken}[by={Barbie}]
\beginverse
\[D]Doesn't se\[G]em to matter w\[C]hat I do, I'm always \[Em]number two
No one kn\[C]ows how hard I tried, oh
\[D]I, I have fe\[G]elings that I \[C]]can't explain, they're drivin' m\[Em]e insane
All my li\[C]fe been so polite but I'll sleep alone tonight

\endverse 
\beginchorus
'Cause \[A]I'm \[E/G#]just \[F#mi]Ken, anywhere else I'd be a te\[A]n
Is it my destiny to \[E]live and die a li\[D]fe of blonde fragi\[A]lity?
\[A]I'm \[E/G#]just  \[F#m]Ken, where I see love, she sees a fri\[A]end
What will it take for her to s\[E]ee the man be\[D]hind the tan and fi\[A]ght for me?

\[E] \[G] \[D]
\[E] \[G] \[D]
\[E] \[G] \[D] \[A]

\endchorus
\beginverse

\[E]   I wan\[G]na know what it’s like to \[D]love
To be the r\[E]eal thing
Is it a cri\[G]me? Am I not \[D]hot when I'm in my fe\[E]elings?
And is my mo\[G]ment finally he\[D]re or am I dr\[A]eaming?
\[A]I'm no dr\[Em]eamer

\[Cm] \[Bb]
\[Cm] \[Bb]
\[Cm] \[Bb]
\[Cm] \[Bb]

\endverse

\beginverse
\[Cm]   Can you feel the Ken-ergy? \[F] \[Fm]
\[Cm]Feels so real, my Ken-ergy \[F] \[Fm]
\[Cm]Can you feel the Ken-ergy?\[F] \[Fm]
\[Cm]Feels so real, my Ken-ergy\[F] \[Fm] \[F#]

\endverse


\beginchorus

\[B]I'm \[F#/A#]just \[G#m]Ken, anywhere else I'd be a \[B]ten
Is it my destiny to \[F#]live and die a \[E]life of blonde fragi\[B]lity?
\[B]I'm \[F#/A#]just  \[G#m]Ken, where I see love, she sees a fri\[B]end
What will it take for her to \[F#]see the man be\[E]hind the ten and fi\[B]ght for me?


\endchorus
\beginchorus

\[B]I'm \[F#/A#]just  \[G#m]Ken and I'm enough and I'm g\[B]reat at doing stuff
So, hey,\[F#] check me \[E]out, yeah, I'm just \[B]Ken
\[B]My na\[F#/A#]me's \[G#]Ken (And so am I), put that \[B]manly hand in mine
So, \[F#]hey, world, check me \[E]out, yeah, I'm just \[B]Ken
Baby, \[B]I'm \[Bm]just \[F#]Ken

\endchorus
\end{song}

